---
title: "HW4_fish_data"
author: "Ruoyuan Li"
date: "February 16, 2018"
output: pdf_document
---

*BMB*: it's good to name all your R code chunks.



First load package and data.
```{r load_stuff,message=FALSE}
library(readr)
library(reshape2) ## BMB: why not tidyr?
library(tidyverse)
library(directlabels)

fish_data <- read_csv("fish.csv",col_names = TRUE)
colnames(fish_data)[3] <- "SampleID"
## BMB: could also use names(fish_data) <- make.names(fish_data)
##  or dplyr::rename()
## BMB: col_names=TRUE is the default value ...
fish_name <- read_csv("fish_names.csv",col_names = TRUE)
```

Switch wide format to long format, and merge the two data sets together. Now the full data has all the information for plotting.
```{r}
#wide format to long format
fish_long <- melt(fish_data, id.vars = c("SampleID", "Site","MetCode","SamplerType"),
     variable.name = "treatment_variable", 
     value.name = "treatment_value")

#merge name data with  long format data.
fish_name$treatment_variable<- fish_name$abbr
full<-merge(fish_long, fish_name)
(full%>%select(-abbr))->full
```

First plot showing under the same drugcat, how drug changes with Site.  Like under drugcat is food, SUC always have higher value for each Site than CFN, same happen to antidepressant, and antibiotic. However, like with drugcate is beta-blocker, ATN has higher value than PPN for both Site: Downstream and Outfall, but PPN higher than ATN for site:WWTP.
```{r plot1,fig.width=8,fig.height=8}
p1<-(ggplot(full,aes(x=Site,y=treatment_value,colour=treatment_variable))
     +geom_point(alpha=0.3)
     +facet_wrap(~drugcat,labeller = label_both,scale = "free_y"))

print(p1+geom_line(aes(group=treatment_variable))
   +geom_dl(aes(label=treatment_variable),,method="last.points")
   +theme(axis.text.x = element_text(angle = 60, hjust=1))
   +theme(legend.position="none")
)
```

*BMB*: I adjusted the justification with `hjust` to align the x-axis labels
more neatly, and adjusted the width and height of the figure
(`fig.width` and `fig.height` chunk options). I made only the y-axis
scales free (since the x-axis labels are shared).

- What about a nicer x axis label?
- The lines through the points don't
quite work; you should probably compute the mean for each chemical
$\times$ site combination, then use that reduced data set to draw lines.
- Do you really need `label_both` here? I'd say it's reasonably clear
what the labels represent 

Second plot is drug's value for each Site. SUC has much higher value for each Site except Control. Compared to the other Sites, control has fewer changes for each drug. 
```{r}
p2<-ggplot(full,aes(x=treatment_variable,y=treatment_value,colour=Site))
print(p2+geom_line(aes(group=Site))+facet_wrap(~Site,labeller = label_both)
      +geom_point()
      +theme(axis.text.x = element_text(angle = 60))
      +theme(legend.position="none"))

print(p2+geom_line(aes(group=Site))+facet_wrap(~Site,labeller = label_both,scales = "free")
      +geom_point()
      +theme(axis.text.x = element_text(angle = 60))
      +theme(legend.position="none"))
```

This seems fine. How did you decide to order

