---
title: "Spatial_Data"
author: "Ruoyuan Li"
date: "March 28, 2018"
output: html_document
---

* trying some example crime data through `ggmap`, always failed at `get_map`, not sure what happened. For this assignment, have no idea how to do it well. but it looks fancy with map. 

* checked some leaflet example online [here](https://rstudio.github.io/leaflet/showhide.html)

* the truth is for now it is hard to come up with fancy plot, it is rarely used in my daily life, so it is hard to interprete a good plot except simple things like call a city name and show the map.

* summary of learning: I realized spatial data is useful for earth science, environment science study. Anything related to location will be useful to interprete with spatial data. I never use data with lat and long, so it is hard to learn and apply immediately. But it is nice way to show more information with location specified data. 


```{r message=FALSE}
library(leaflet)
library(forcats)
library(labeling)
library(ggmap)
library(tidyverse)
library(skimr)
library(rgdal)

```


```{r}
skim(quakes)
quakes <- quakes %>%
  dplyr::mutate(mag.level = cut(mag,c(3,6),
                                labels = c('>3 ')))


quakes.df <- split(quakes, quakes$mag.level)

l <- leaflet() %>% addTiles()

## BMB: what is this doing??? It's good that you cited your sources,
##  but can you say anything about what any of the code means??
names(quakes.df) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=quakes.df[[df]],
                 lng=~long, lat=~lat,
                 label=~as.character(mag),
                 popup=~as.character(mag),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(
    overlayGroups = names(quakes.df),
    options = layersControlOptions(collapsed = FALSE)
  )
```

```{r}
paris <- get_map(location = "paris")
str(paris)
ggmap(paris, extent = "normal")
```
